\documentclass[10pt,conference]{IEEEtran}
% If the IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it:
% \documentclass[conference]{../sty/IEEEtran}

\begin{document}

% paper title
\title{Instructions for Preparation and Submission of Papers for NCC 2019}

% make the title area
\maketitle

\begin{abstract}
This note provides instructions for the preparation of papers
for submission to NCC 2019, and the relevant style file that produced
this page.
\end{abstract}

\section{Introduction}
NCC 2019 will be held at the ECE Department in the 
Indian Institute of Science (IISc), Bangalore, India, from Thursday, Feb.~20 to
Saturday, Feb.~23, 2019.



\section{Submission and Review Process}
Papers will be reviewed on the basis of a manuscript of sufficient
detail to permit reasonable evaluation. The manuscript should {\bf
not exceed {\bf SIX} double-column pages, with single line spacing, main
text font size no smaller than 10 points, and at least 0.5 inch
margins}. The deadline for submission is {\bf Saturday, Sep. 15, 2018}, with notification of decisions by {\bf Friday, Nov. 30, 2018}. The deadline for the final camera-ready paper is {\bf Sunday, Dec. 30, 2018}. 
Final manuscript guidelines will be made available after the notification of decisions.


{\bf{Important Note:}} 
All submitted papers will be judged based on their quality and relevance through {\bf double-blind reviewing}, where the identities of the authors are withheld from the reviewers. As an author, you are required to preserve the anonymity of your submission, while at the same time allowing the reader to fully grasp the context of related past work, including your own. Common sense and careful writing will go a long way towards preserving anonymity. Papers that do not conform with our double-blind submission policies will be rejected without review.

Note that, with double blind submissions and reviews, the only way the TPC Chairs will know the authors of a paper is if {\bf all authors are listed in the EDAS portal,} as this information is not available in the PDF. Therefore, it is very important to include all authors in the EDAS portal. To do this, after registering the title, abstract and topics for the paper on EDAS, in the second page, you MUST add all authors who contributed to the paper. {\bf The TPC Chairs will not be able to add authors after paper acceptance.} 

%\section{Proceedings}
%All the accepted papers will be published in a conference
%proceeding. All the registrants at the conference will receive a
%copy of the proceedings.

\section{Preparation of the Paper}
Only electronic submissions in the form of a Postscript (PS) or Portable
Document Format (PDF) file will be accepted. Most authors will
prepare their papers with \LaTeX. The \LaTeX\ style file
(\verb#IEEEtran.cls#) and the \LaTeX\ source
(\verb#ncc2019_example.tex#) that produced this page may be
downloaded from the NCC 2019 web site
(http://ece.iisc.ernet.in/$\sim$ncc2019). Do not change the style file
in any way. 
Authors using other means to prepare their manuscripts
should attempt to duplicate the style of this example as closely as
possible.

The style of references, 
e.g.,
\cite{Shannon1948},\cite{Kalman1960},\cite{Rao2008},\cite{Mhatre2009}, 
equations, figures, tables, etc.,
should be the same as for the \emph{IEEE Transactions on Information
Theory}. 
%The affiliation shown for authors should constitute a
%sufficient mailing address for persons who wish to write for more
%details about the paper.

\section{Electronic Submission}
The paper submission portal is EDAS:
\begin{itemize}
\item Communications Track:

{\texttt{https://edas.info/newPaper.php?\\c=25340\&track=92756}}

\item Networks Track:

{\texttt{https://edas.info/newPaper.php?\\c=25340\&track=92757}}

\item Signal Processing Track:

{\texttt{https://edas.info/newPaper.php?\\c=25340\&track=92758}}
\end{itemize}

For relevant announcements please check the NCC 2019 website
(http://ece.iisc.ernet.in/$\sim$ncc2019).

\section{Conclusion}
Conclusions, if any, go here.

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}
% optional entry into table of contents (if used)
%\addcontentsline{toc}{section}{Acknowledgment}
We thank everyone who helped us. 

\begin{thebibliography}{1}

\bibitem{Shannon1948}
C.~E.~Shannon, ``A mathematical theory of communication,''
\emph{Bell Syst.\ Tech.\ J.}, vol.\ 27, pt.~I, pp.~379--423, 1948;
     pt.~II, pp.~623--656, 1948.

\bibitem{Kalman1960}
R.~E.~Kalman, ``A new approach to linear filtering and prediction
problems,'' \emph{Journal of Basic Engineering}, vol.\ 82, no.\ 1,
pp.~35--45, 1960.

\bibitem{Rao2008}
K.~S.~Rao, ``Indian Institute of Science Campus: A Botanist's
Delight,'' Bangalore: IISc Press, 2008.

\bibitem{Mhatre2009}
N.~Mhatre, ``Secret Lives: Biodiversity of the Indian Institute of
Science Campus,'' Bangalore: IISc Press, 2009.

\end{thebibliography}


\end{document}
